Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-02 presentation-plan/Plan_presentation_monday.tex
Add a small example for a simple planning problem.

Planning Problem:

\begin{itemize}
	\item Initial State
	\item Goal State
	\item Set of actions
\end{itemize}

Planning Plan:

>>>>

\begin{figure}[htb]%
\includegraphics[width=0.4\columnwidth]{blocksworld.pdf}%
\caption{Blocks World example (Figure from~\url{http://www.cs.utexas.edu/~mooney/cs343/slide-handouts/planning.4.pdf})}%
\label{fig:blocksworld}%
\end{figure}

In figure~\ref{fig:blocksworld}, how do you go from the initial state to the
goal state? First you have to move A from B, before you can put B on C and
finally A on B. This is a very trivial example of planning. Between each
action of moving a block, the world is in a certain state. Actions provide
a way to go from one state to another, but from each state, it is possible
to do multiple actions. For example in the initial state you can move C onto
A, but that doesn't help achieving the goal. Finding the right sequence of
actions is what a planner does. From this we can define:

\noindent \textbf{Planning Problem}:

\begin{itemize}
	\item Initial State
	\item Goal State
	\item Set of actions
	\item Conditions
\end{itemize}

\noindent And the \textbf{Planning Plan}:
